Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2021-01-09 submission/NatCom_appendix.tex
appendix plots updates

%\section{Reproducibility Appendix}
\section{Supplementary Information}
\label{sxn:appendix}

@@

See
Figure~\ref{fig:summary_regressions_A},
Figure~\ref{fig:summary_regressions_B},
Figure~\ref{fig:summary_regressions_C},
Figure~\ref{fig:summary_regressions_D},
Figure~\ref{fig:summary_regressions_E},
Figure~\ref{fig:summary_regressions_F},
Figure~\ref{fig:summary_regressions_G},
Figure~\ref{fig:summary_regressions_H}, and
Figure~\ref{fig:summary_regressions_I} for more details.
\michael{Charles, would you put a bit of discussion, e.g., on best and worst, again just a teaser to satisfy that reviewer.}

>>>>

>%\section{Reproducibility Appendix}
\section{Supplementary Information}
\label{sxn:appendix}

@@

See
Figure~\ref{fig:summary_regressions_A},
Figure~\ref{fig:summary_regressions_B},
Figure~\ref{fig:summary_regressions_C},
Figure~\ref{fig:summary_regressions_D},
Figure~\ref{fig:summary_regressions_E},
Figure~\ref{fig:summary_regressions_F},
Figure~\ref{fig:summary_regressions_G},
Figure~\ref{fig:summary_regressions_H}, and
Figure~\ref{fig:summary_regressions_I} for more details.
\michael{Charles, would you put a bit of discussion, e.g., on best and worst, again just a teaser to satisfy that reviewer.}
From these Figures, we recognize fits of varying quality, ranging from remarkably good to completely uncorrelated.
Starting with the best, consider the Imagenet-1K PreResNet results.  Figure~\ref{fig:summary_regressions_A_10} shows 
the Avg. Log Spectral Norm $\langle\log\Vert\mathbf{W}\Vert^{2}_{\infty}\rangle$, 
which has a rather large $RMSE=3.93$, and rather small $R2=0.36$, and Kendal-$\tau=0.54$, and
has 6 out of 13 points outside the $95\%$ confidence bands.  In contrast, 
the Avg. Log Alpha Norm $\langle\log\Vert\mathbf{W}\Vert^{\alpha}_{\alpha}\rangle$, 
in  Figure~\ref{fig:summary_regressions_A_12} , 
has a much smaller $RMSE=1.93$, and much larger  $R2=0.85$, and Kendal-$\tau=0.87$, 
and only 2 points outside the $95\%$ confidence bands.
For examples of lower quality fits, consider the SqueezeNext results, as shown Figures~\ref{fig:summary_regressions_C_10} and 
~\ref{fig:summary_regressions_C_12}.  
The Avg. Log Spectral Norm $\langle\log\Vert\mathbf{W}\Vert^{2}_{\infty}\rangle$,
is visually anti-correlated  with the test accuracies
(as it is with ShuffleNet, in Figure ~\ref{fig:summary_regressions_B_02}).
with a very large $95\%$ confidence band, with only 2 points close to the regression line,
a large RMSE,  $R2=0.07$ (i.e zero), and small Kendal-$\tau=0.33$.
The Avg. Log Alpha Norm $\langle\log\Vert\mathbf{W}\Vert^{\alpha}_{\alpha}\rangle$ is always positively-correlated
with test accuracies, but with $R2=43$, which is not great--but not zero, and a reasonable Kendal-$\tau=0.73$.
